HW #4: Analyze real-world emissions data

### 2022-11-18 HW4/HW4.Rmd
update hw4

feat1 %>% 
	ggplot() +
	geom_density(aes(x = amount, color = pollutant)) +
	facet_wrap(~DATE) +
	lims(x = c(NA,200),
			 y = c(NA,0.1)) +
	labs(x = "Emmission Rate (g / kg fuel)",
			 y = "kernel density",
			 color = "Pollutant")
```

@@

fit2 %>% 
	tidy() %>% 
	kbl(booktabs = TRUE, digits = c(0,2,2,2,3), escape = FALSE) %>% 
	footnote(paste0("$R^2$ = ", fit2$adj.r.squared %>% round(3)),
					 general_title = "") %>% 
	kable_styling(latex_options = "HOLD_position")
```

@@

```{r}
feat1 %>% 
	filter(pollutant == "CO") %>% 
	select(-pollutant, -VEH_ID) %>% 
	group_by(DATE, location) %>% 
	summarise(
		name = names(MeanCI(amount, conf.level = 0.9)),
		value = MeanCI(amount, conf.level = 0.9)) %>% 
	pivot_wider()
```

```{r}
feat1 %>% 
	filter(pollutant == "CO") %>% 
	select(-pollutant, -VEH_ID) %>% 
	ggplot(aes(y = DATE, x = amount, fill = location)) +
	geom_violin() +
	stat_summary(
		fun.data = function(x) MeanCI(x, conf.level = 0.9) %>% 
			`names<-`(c("y", "ymin", "ymax")),
		geom = "errorbar",
		width = 0.3) +
	stat_summary(fun = mean, geom = "point")
```

>>>>

feat1 %>% 
	ggplot() +
	geom_density(aes(x = amount, color = pollutant)) +
	facet_wrap(~DATE) +
	theme_pander() +
	lims(x = c(NA,100),
			 y = c(NA, 0.3)) +
	labs(x = "Emmission Rate (g / kg fuel)",
			 y = "kernel density",
			 color = "Pollutant")
```

@@

fit2 %>% 
	tidy() %>% 
	kbl(booktabs = TRUE, digits = c(0,2,2,2,3)) %>% 
	footnote(paste0("$R^2$ = ", fit2$adj.r.squared %>% round(3)),
					 general_title = "",
					 escape = FALSE) %>% 
	kable_styling(latex_options = "HOLD_position")
```

@@

```{r}
feat1 %>% 
	filter(pollutant == "CO") %>% 
	select(-pollutant, -VEH_ID) %>% 
	group_by(DATE, location) %>% 
	summarise(
		name = names(MeanCI(amount, conf.level = 0.9)),
		value = MeanCI(amount, conf.level = 0.9)) %>% 
	pivot_wider() %>% 
	kbl(booktabs = TRUE, digits = c(0,0,2,2,1)) %>% 
	kable_styling(latex_options = "HOLD_position")
```

```{r}
#| mean-conf,
#| fig.cap = "CO emission rate for each day. The bars show the mean and 90% confidence interval for the mean.",
#| fig.pos = "H",
#| fig.height = 3

feat1 %>% 
	filter(pollutant == "CO") %>% 
	select(-pollutant, -VEH_ID) %>% 
	ggplot(aes(y = DATE, x = amount, fill = location)) +
	geom_violin() +
	stat_summary(
		fun.data = function(x) MeanCI(x, conf.level = 0.9) %>% 
			`names<-`(c("y", "ymin", "ymax")),
		geom = "errorbar",
		width = 0.3) +
	stat_summary(fun = mean, geom = "point") +
	theme_pander() +
	xlim(NA, 200) +
	labs(
		x = "CO Emission Rate (g / kg fuel)",
		y = "Date",
		fill = "Location")
```

```{r}
feat1 %>% 
	filter(pollutant == "CO") %>% 
	aov(amount ~ location, data = .) %>% 
	TukeyHSD()
```
